Analysis: NAME

### 2019-12-07 tsq_data.Rmd
initial commit

```{r}
results <- all_data %>% select(-injection_details) %>% unnest(integration_results) %>% 
  filter(nchar(`Peak Name`) > 0)

@@

```{r}
results %>% 
  left_join(
    tibble(
      `Peak Name` = c("19:0", "23:0"), 
      group = c("19", "23")
    ), by = "Peak Name"
  ) %>% 
  ggplot() +
  aes(`Retention Time`, `Relative Height`, fill = group, label = `Peak Name`) +
  geom_bar(stat = "identity") +
  facet_grid(sample ~ .) +
  theme_figure() +
  scale_y_continuous(expand = c(0, 0))
```

@@

>>>>

```{r}
results <- all_data %>% 
  select(-injection_details) %>% 
  unnest(integration_results) %>% 
  filter(nchar(`Peak Name`) > 0) %>% 
  # major compound groups
  mutate(
    group = `Peak Name` %>% str_remove("\\d+-OH") %>% parse_number() %>% abs() %>% {paste0("C", .)} %>% factor()
  )

@@

```{r}
results %>% 
  ggplot() +
  aes(`Retention Time`, `Relative Height`, fill = group, label = `Peak Name`) +
  geom_bar(stat = "identity") +
  facet_grid(sample ~ .) +
  theme_figure(legend = TRUE) +
  scale_y_continuous(expand = c(0, 0))
```

@@

# export data

```{r}
results %>% 
  filter(sample == "a") %>% 
  mutate(rt = `Retention Time` * 60) %>% 
  select(group, `Peak Name`, rt, rel_height = `Relative Height`) %>% 
  mutate(rt = round(rt, 1), rel_height = round(rel_height, 2)) %>%
  filter(rel_height > 1) %>% 
  openxlsx::write.xlsx(file.path("tables", "tsq_single_sample_peak_table.xlsx"))
```
